---
title: "BC Ambient"
author: "Adithi"
date: "5/29/2020"
output: github_document
---
  
```{r setup, include=FALSE}
library(shiny)
library(DT)
library(plotly)
library(lubridate)
library(data.table)
library(zoo)
library(xts)
library(data.table)
library(stringr)
library(dplyr)
library(ggplot2)
library(readr)
library(tidyverse)
library(keyring)
library(leaflet)
library(htmltools)
library(lubridate) # Timestamp maniupulation
library(raster)
library(rgdal)
library(sp)
library(sf)
library(scales)
library(mailR)
library(blastula)
library(rsconnect)
library(caTools)
library(curl)
library(devtools)
library(XML)
library(openair)
library(purrr)

############# Wrap Function
Correlation <- function(y, x, data, lm, a, b, c, x_axi, y_axi) {
  Mean_y<-round(mean(y, na.rm=TRUE), digits = 1)
  Mean_x<-round(mean(x, na.rm=TRUE), digits = 1)
  Median_y<-round(median(y, na.rm=TRUE), digits = 1)
  Median_x<-round(median(x, na.rm=TRUE), digits = 1)
  
  m<-lm(y~x)
  s<-summary(m)
  r<-summary(lm(y~x))
  r$r.squared<-round(r$r.squared, digits=2)
  n<-nrow(data)
  data$diffSq<-(y-x)*(y-x)
  
  mean_diff_sqr<-mean(data$diffSq, na.rm = TRUE)
  rmse<-sqrt(mean_diff_sqr)
  rmse<-round(rmse, digits = 2)
  
  p_correlation<-ggplot(data=data,
                        aes(x=x, y=y))+
    geom_point(alpha=1,size=2.2)+theme_minimal()+
    geom_smooth(method=lm, se=FALSE, formula = y~x)+
    geom_abline(slope=1, intercept=0, color="black", size=0.8, linetype="dashed")+
    labs(x=x_axi,
         y= y_axi,
         title= paste0("R square: ", r$r.squared),
         subtitle= paste0("Fig: RMSE: ", rmse, "; Mean(Median)-", " Y=", Mean_y,"(",Median_y, ")", "; X=", Mean_x,"(",Median_x, ")", " (ug/m3);"))+ annotate("text", label = reg_eqn(s), x =a, y = b) +theme(legend.text=element_text(size=12),plot.title = element_text(size = 14, face = "bold"),plot.subtitle = element_text(size = 10, face = "bold"), axis.title = element_text(size=18),axis.text = element_text(size = 16, face = "bold"), panel.border = element_rect(colour = "black", fill=NA, size=1.2))+scale_x_continuous(limits=c(0,c))+scale_y_continuous(limits=c(0,c))
  return(p_correlation)
}
f <- function(x) {
  r <- quantile(x, probs = c(0.05, 0.25, 0.5, 0.75, 0.95))
  names(r) <- c("ymin", "lower", "middle", "upper", "ymax")
  r
}
reg_eqn<-function(x){
  R_sq<-round(as.numeric(x$adj.r.squared), digits =2)
  int<-round(coef(x)[1], digits=2)
  slope<-round(coef(x)[2], digits=2)
  eqn<-paste("y=", slope,"x+(",int, ")")
  return(eqn)}
completeFun <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}
```

## Black Carbon (BC) Ambient Measurements at CSTEP and ILK Labs

The instruments used: 

- at ILK Labs : Loading Corrected AE51 (30 mins before and after the ride)

- at CSTEP : AE33 (24 hours)

```{r warning=FALSE, message=FALSE, results=FALSE, include=FALSE}
setwd("D:/Dropbox/APMfull/ISI - Ambient Readings/Ambient_ILK_Con_2019/Aethalometer")
dir="D:/Dropbox/APMfull/ISI - Ambient Readings/Ambient_ILK_Con_2019/Aethalometer"
lt <- list.files(dir, pattern = "\\.csv$")
data_final_BC<-data.frame()

for (z in (lt)) 
{
  trial<- read.csv(z, header=TRUE, skip = 16, sep=",")
  trial$Date <- with(trial, as.POSIXct(paste(as.Date(Date, format="%Y/%m/%d"), Time)))
  dtPOSIXct <- as.POSIXct(trial$Date )
  dtTime <- as.numeric(dtPOSIXct - trunc(dtPOSIXct, "days"))
  class(dtTime) <- "POSIXct"
  ef<-data.frame(trial)
  ef<-ef[ef$Status==0,]
  ef<-dplyr::select(ef, Date, ATN, BC)
  # ATN<-ef[1,2]
  # ef$ATN<-ef$ATN-(ATN)
  ef$BC1<-(ef$BC/1000)
  ef$LD<- ef$BC1-rollapply(ef$BC1 , FUN = mean, width = 30, align="center", partial=TRUE)
  ef$LD25<-runquantile(ef$LD, 300, 0.25, type=2, endrule=c("NA"))
  ef$LD75<-runquantile(ef$LD, 300, 0.75, type=2, endrule=c("NA"))
  ef$BC2<-ef$BC1
  ef$BC2[ef$BC2>=0]<-0
  ef$BC2[ef$BC2<0]<-1
  ef$BC2<-rollapply(ef$BC2 , FUN = mean, width = 5, align="center", partial=TRUE)
  a<-((ef$LD)>5*(ef$LD75))
  b<-((ef$LD)< 5*(ef$LD25))
  ef$cev1<-ifelse(a|b,ef$BC1,NA)
  ##kf<-xts(ef, order.by = ef$Date)
  
  CEV<-data.frame(ef$Date, ef$cev1)
  CEV$ef.cev1[!is.na(CEV$ef.cev1)] <-1
  ##CEV$ef.Date<-na.omit(CEV$ef.cev1)
  CEV<-data.frame(CEV)
  xt<-data.frame(ef$Date,  ef$BC2)
  completeFun <- function(data, desiredColumns) {
    completeVec <- complete.cases(data[, desiredColumns])
    return(data[completeVec, ])
  }
  CEV<-completeFun(CEV, c("ef.cev1"))
  setDT(CEV)
  setDT(xt)
  fe<-xt[CEV, on = c('ef.Date')]
  fe<-fe[!(fe$ef.BC2==0),]
  fe<-xts(fe, order.by = fe$ef.Date)
  ef<-data.frame(ef)
  CE<-data.frame(index(CEV))
  i=index(fe)
  i_old=index(fe)
  i=index(fe)+1
  j=index(fe)+2
  k=index(fe)-2
  l=index(fe)-1
  i<-cbind(as.character(i),as.character(i_old), as.character(j), as.character(k), as.character(l))
  Date_T1<-data.frame(i)
  d1 <- data.frame(Date=unlist(Date_T1, use.names = FALSE))
  Date_T<-unique(d1[c("Date")])
  print("works till here")
  e=nrow(Date_T)
  if(e == 0){
    print("data.frame is empty")
    Da<-ef
    Da$BC_Factor<- 1
  }else{
    Date_T$BC_Factor<-0
    Date_T$Date<-as.POSIXct(Date_T$Date)
    setDT(Date_T)
    setDT(ef)
    Da<-Date_T[ef, on = c('Date')]
    Da$BC_Factor[is.na(Da$BC_Factor)] <- 1
    print("data.frame contains data")
  }
  Da$BC_Fi<-Da$BC_Factor*Da$BC1
  Da$BC_Fi[Da$BC_Fi == 0] <-NA
  Da$Tr=exp(-Da$ATN/100)
  Da$CF=1/(0.88*Da$Tr+0.12)
  Da$BC_Final=Da$BC_Fi*Da$CF
  Da$BC_Final[Da$BC_Final<0]<-NA
  Da$BC_Final[is.na(Da$BC_Final)] <- " "
  BC<-data.frame(Da$Date,Da$BC_Final)
  colnames(BC) <- c("Date", "BC")
  data_final_BC<-rbind(data_final_BC, BC)
  # myOutFile =paste("D:/Delhi_microAeth_AE38_site1/Corrected_BC_",z)
}
data_final_BC$hour<-lubridate::ceiling_date(data_final_BC$Date, "hour")
data_final_BC$BC<-as.numeric(as.character(data_final_BC$BC))
data_final_BC1<-data_final_BC%>%
  dplyr::select(hour, BC)%>%
  group_by(hour)%>%
  summarise(mean_BC_mm=mean(BC, na.rm = TRUE))


setwd("D:/Dropbox/APMfull/Colocation CSTEP/CSTEP_co-location_2020/Exp_9_2020_01_15/AE33_CSTEP")
ae33_cstep<-data.frame()
dir<-"D:/Dropbox/APMfull/Colocation CSTEP/CSTEP_co-location_2020/Exp_9_2020_01_15/AE33_CSTEP/"
shp_list1<- list.files(dir, pattern="\\.dat$")
for (fil in (shp_list1)) {
  ae33_1<- read.table(paste("D:/Dropbox/APMfull/Colocation CSTEP/CSTEP_co-location_2020/Exp_9_2020_01_15/AE33_CSTEP/", fil, sep =""), header=TRUE, skip= 4)
  ae33_1<-data.frame(ae33_1)
  ae33_1$date <- with(ae33_1, as.POSIXct(paste(as.Date(Date.yyyy.MM.dd.., format="%Y/%m/%d"), Time.hh.mm.ss..)))
  ae33_1$BC6.<-ae33_1$BC6./1000
  ae33_1$BC1.<-ae33_1$BC1./1000
  ae33_1<-ae33_1[ae33_1$Status.==0||ae33_1$Status.==256||ae33_1$Status.==128,]
  ae33_1<-dplyr::select(ae33_1, date,BC6., BC1.)
  
  ae33_cstep<-rbind(ae33_cstep, ae33_1)
}
names(ae33_cstep)<-c("date", "AE33_cstep", "UVPM_cstep")


Final<-data.frame(ae33_cstep)
Final<-Final[Final$AE33_cstep > 0.000, ]
Final<-Final[Final$UVPM_cstep > 0.000, ]
Final$month<-format(Final$date, "%m")
Final$hour<-lubridate::ceiling_date(Final$date, "hour")
Final$Date<- as.Date(as.POSIXct(Final$date,tz="Asia/Kolkata"),tz="Asia/Kolkata")
Final<-Final[Final$Date!="2019-08-13",]
Final<-Final[Final$Date!="2019-08-14",]
Final<-Final[Final$Date!="2019-08-18",]
Final<-Final[Final$Date!="2019-08-19",]
Final<-Final[Final$Date!="2019-08-20",]
Final<-Final[Final$Date!="2019-08-21",]
Final<-Final[Final$Date!="2019-08-30",]
Final<-Final[Final$Date!="2019-08-31",]
Final<-Final[Final$Date!="2019-09-01",]
Final<-Final[Final$Date!="2019-09-02",]
Final1<-Final%>%
  dplyr::select(hour, AE33_cstep)%>%
  group_by(hour)%>%
  summarise(mean_AE33_cstep=mean(AE33_cstep, na.rm = TRUE))

setDT(Final1)
setkey(Final1, hour)
setDT(data_final_BC1)
setkey(data_final_BC1, hour)
BC<-merge(data_final_BC1, Final1,by = "hour", all = TRUE)
BC<-data.frame(BC)
BC<-completeFun(BC, c("mean_BC_mm"))
BC<-completeFun(BC, c("mean_AE33_cstep"))
BC<-BC[BC$mean_BC_mm<50,]
names(BC)<-c("hour", "LC_AE51_ILK", "AE33_CSTEP")

```

## Days of measurement- Start Date

- AE51: 14 May 2019

_Average of ambient hour_

```{r   message=FALSE, warning=FALSE}
names(data_final_BC1)<-c("date", "LC_AE51_ILK")
calendarPlot(data_final_BC1, pollutant = "LC_AE51_ILK")
```

- AE33: 11 July 2019

_24 hour average_

```{r   message=FALSE, warning=FALSE}
names(Final1)<-c("date", "AE33_CSTEP")
calendarPlot(Final1, pollutant = "AE33_CSTEP")
```

## Correlation plot

From here on, the data for both AE33 and AE51 were filtered where both the data were present ie: starting from July 11 2019 to 19 February 2020. The hours of AE51 were matched with corresponding hours of AE33.

- LC_AE51_ILK: Loading corrected AE51 measurements of BC

- AE33_CSTEP: AE33 measurements of BC

```{r   message=FALSE, warning=FALSE}
t<- Correlation(BC$AE33_CSTEP, BC$LC_AE51_ILK, BC, lm, 5, 25, 30, "LC_AE51_ILK", "AE33_CSTEP")
t
```

## t-test

```{r   message=FALSE, warning=FALSE}
t.test(BC$LC_AE51_ILK,BC$AE33_CSTEP )
```

## Box Plot


```{r  message=FALSE, warning=FALSE}
BC_melt<-reshape2::melt(BC, id="hour", measure.vars = c( "LC_AE51_ILK",  "AE33_CSTEP") )
names(BC_melt)<-c("hour","Instrument", "BC")
p1<-ggplot(BC_melt, aes(Instrument, BC))+ 
  labs(x="", y= expression(paste("BC" ," (", mu, "g",~m^{-3}, ")")),title=paste0(""))+
  stat_summary(fun.data = f, geom="boxplot", width=0.2, size=1.2)+  
  stat_summary(fun.y=mean, colour="black", geom="point",size=4)+
  scale_y_continuous(limits = c(0,15), expand = c(0, 0))+theme_minimal()+
  theme(legend.text=element_text(size=14),plot.subtitle = element_text(size = 10, face = "bold"),
        plot.title = element_text(size = 12, face = "bold"), 
        axis.title = element_text(size=28, face="bold"),axis.text = element_text(size = 28, colour = "black",face = "bold"),
        panel.border = element_rect(colour = "black", fill=NA, size=1.2),axis.text.x = element_blank() ) + annotate("text", label = "LC_AE51_ILK", x ="LC_AE51_ILK", y =14, size=6, face="bold")+ annotate("text", label = "AE33_CSTEP", x ="AE33_CSTEP", y =14, size=6, face="bold")
p1


```

## Time Variations

- LC_AE51: Loading corrected AE51 measurements of BC

- AE33: AE33 measurements of BC


1. For the weekday and hours  

```{r   message=FALSE, warning=FALSE, results=FALSE}
names(BC)<-c("date", "LC_AE51", "AE33")
BC_timeVari<-timeVariation(BC, pollutant=c("AE33", "LC_AE51"))
plot(BC_timeVari, subset = "day.hour") 
```


2. For the diurnal plot

```{r   message=FALSE, warning=FALSE}
plot(BC_timeVari, subset="hour") 
```

3. For the weekday plot

```{r   message=FALSE, warning=FALSE}
plot(BC_timeVari, subset="day") 
```

4. For the monthly plot

```{r   message=FALSE, warning=FALSE}
plot(BC_timeVari, subset="month") 

```
