---
title: "PM 2.5 Ambient"
author: "Adithi"
date: "5/30/2020"
output: github_document
---

```{r setup, include=FALSE}
library(shiny)
library(DT)
library(plotly)
library(lubridate)
library(data.table)
library(zoo)
library(xts)
library(data.table)
library(stringr)
library(dplyr)
library(ggplot2)
library(readr)
library(tidyverse)
library(keyring)
library(leaflet)
library(htmltools)
library(lubridate) # Timestamp maniupulation
library(raster)
library(rgdal)
library(sp)
library(sf)
library(scales)
library(mailR)
library(blastula)
library(rsconnect)
library(caTools)
library(curl)
library(devtools)
library(XML)
library(purrr)
library(openair)

############# Wrap Function
Correlation <- function(y, x, data, lm, a, b, c, x_axi, y_axi) {
  Mean_y<-round(mean(y, na.rm=TRUE), digits = 1)
  Mean_x<-round(mean(x, na.rm=TRUE), digits = 1)
  Median_y<-round(median(y, na.rm=TRUE), digits = 1)
  Median_x<-round(median(x, na.rm=TRUE), digits = 1)
  
  m<-lm(y~x)
  s<-summary(m)
  r<-summary(lm(y~x))
  r$r.squared<-round(r$r.squared, digits=2)
  n<-nrow(data)
  data$diffSq<-(y-x)*(y-x)
  
  mean_diff_sqr<-mean(data$diffSq, na.rm = TRUE)
  rmse<-sqrt(mean_diff_sqr)
  rmse<-round(rmse, digits = 2)
  
  p_correlation<-ggplot(data=data,
                        aes(x=x, y=y))+
    geom_point(alpha=1,size=2.2)+theme_minimal()+
    geom_smooth(method=lm, se=FALSE, formula = y~x)+
    geom_abline(slope=1, intercept=0, color="black", size=0.8, linetype="dashed")+
    labs(x=x_axi,
         y= y_axi,
         title= paste0("R square: ", r$r.squared),
         subtitle= paste0("Fig: RMSE: ", rmse, "; Mean(Median)-", " Y=", Mean_y,"(",Median_y, ")", "; X=", Mean_x,"(",Median_x, ")", " (ug/m3);"))+ annotate("text", label = reg_eqn(s), x =a, y = b) +theme(legend.text=element_text(size=12),plot.title = element_text(size = 14, face = "bold"),plot.subtitle = element_text(size = 10, face = "bold"), axis.title = element_text(size=18),axis.text = element_text(size = 16, face = "bold"), panel.border = element_rect(colour = "black", fill=NA, size=1.2))+scale_x_continuous(limits=c(0,c))+scale_y_continuous(limits=c(0,c))
  return(p_correlation)
}
f <- function(x) {
  r <- quantile(x, probs = c(0.05, 0.25, 0.5, 0.75, 0.95))
  names(r) <- c("ymin", "lower", "middle", "upper", "ymax")
  r
}
reg_eqn<-function(x){
  R_sq<-round(as.numeric(x$adj.r.squared), digits =2)
  int<-round(coef(x)[1], digits=2)
  slope<-round(coef(x)[2], digits=2)
  eqn<-paste("y=", slope,"x+(",int, ")")
  return(eqn)}
completeFun <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}
```

## PM 2.5 Ambient Measurements at CSTEP and ILK Labs

The instruments used were: 
- at CSTEP : BAM 1022
- at ILK Labs : DustTrak 8530 


```{r warning=FALSE, message=FALSE, results=FALSE, include=FALSE}
setwd("D:/Dropbox/APMfull/ISI - Ambient Readings/Ambient_ILK_Con_2019/DustTrak")
dir="D:/Dropbox/APMfull/ISI - Ambient Readings/Ambient_ILK_Con_2019/DustTrak"
lt <- list.files(dir, pattern = "\\.csv$")
data_final_PM<-data.frame()

for (z in (lt))
{
  DT_f<- read.csv(z, header=TRUE, skip = 28, sep=",")
  y<-data.frame(colnames(DT_f))
  date_format<-y[1,1]
  if(date_format=="dd.MM.yyyy")
  {
    names(DT_f)<-c("Date", "Time", "PM2.5")
    DT_f$date <- with(DT_f, as.POSIXct(paste(as.Date(Date, format="%d-%m-%Y"), Time)))
    DT_f$date <- as.POSIXct(DT_f$date, format='%Y-%m-%d %H:%M:%S', tz="Asia/Kolkata")
  }else{
    names(DT_f)<-c("Date", "Time", "PM2.5")
    DT_f$date <- with(DT_f, as.POSIXct(paste(as.Date(Date, format="%m/%d/%Y"), Time)))
    DT_f$date <- as.POSIXct(DT_f$date, format='%Y-%m-%d %H:%M:%S', tz="Asia/Kolkata")
  }
  DT_f$PM2.5<- as.numeric(as.character(DT_f$PM2.5))
  DT_f$PM2.5<-DT_f$PM2.5*1000
  data_final_PM<-rbind(data_final_PM, DT_f)
}
data_final_PM<-data.table(data_final_PM)
setkey(data_final_PM, date)
data_final_PM$hour<-lubridate::ceiling_date(data_final_PM$date, "hour")
data_final_PM$PM2.5<-as.numeric(as.character(data_final_PM$PM2.5))
data_final_PM1<-data_final_PM%>%
  dplyr::select(hour, PM2.5)%>%
  group_by(hour)%>%
  summarise(mean_PM2.5_mm=mean(PM2.5, na.rm = TRUE))


bam<- read.csv(paste("D:/Dropbox/APMfull/Colocation CSTEP/CSTEP_co-location_2020/Exp_10_2020_01-13-27/BAM_DT/","DT145243.CSV", sep =""), skip=4)
bam$Time<- as.POSIXct(bam$Time, format='%d-%m-%Y  %H:%M') 
attributes(bam$Time)$tzone <- "Asia/Kolkata"
bam<-dplyr::select(bam, Time, ConcHR.ug.m3.,ConcRT.ug.m3., FRH..., Status)
names(bam)<-c("date", "BAM","RT_BAM","FRH", "Status")
df_bam_1hr<-bam
df_bam_1hr<- setDT(df_bam_1hr)[order(date)]
df_bam_1hr<- df_bam_1hr[, .(date = date[1], BAM=BAM[1],RT_BAM=RT_BAM[1],FRH=FRH[1], Status=Status[1]) ,                     
             by = .(Group = floor_date(date, "hour"))] 
ix <- which(df_bam_1hr$RT_BAM>=1000 | df_bam_1hr$FRH>45 | df_bam_1hr$BAM<0 |df_bam_1hr$RT_BAM< 0 )
df_bam_1hr<-df_bam_1hr[-c(ix, ix + 1), ]
df_bam_1hr<- df_bam_1hr[df_bam_1hr$Status== 0,]
df_bam_1hr<-df_bam_1hr %>%
  dplyr::select(date, BAM)

df_bam_1hr<-df_bam_1hr[!duplicated(df_bam_1hr$date), ]
Final<-data.frame(df_bam_1hr)
Final$month<-format(Final$date, "%m")
Final$hour<-lubridate::ceiling_date(Final$date, "hour")
Final1<-Final%>%
  dplyr::select(hour, BAM)%>%
  group_by(hour)%>%
  summarise(mean_BAM_cstep=mean(BAM, na.rm = TRUE))
setDT(Final1)
setkey(Final1, hour)
setDT(data_final_PM1)
setkey(data_final_PM1, hour)
PM<-merge(data_final_PM1, Final1,by = "hour", all = TRUE)
PM<-data.frame(PM)
PM<-completeFun(PM, c("mean_PM2.5_mm"))
PM<-completeFun(PM, c("mean_BAM_cstep"))
# PM<-PM[BC$mean_BC_mm<50,]
names(PM)<-c("hour", "DT_ILK", "BAM_CSTEP")

```


## Days of measurement

- BAM: 2 July 2019

```{r   message=FALSE, warning=FALSE}
names(Final1)<-c("date", "BAM_CSTEP")
calendarPlot(Final1, pollutant = "BAM_CSTEP")
```

- DustTrak: 14 May 2019

```{r   message=FALSE, warning=FALSE}
names(data_final_PM1)<-c("date", "DT_ILK")
calendarPlot(data_final_PM1, pollutant = "DT_ILK")
```


## Correlation plot

```{r   message=FALSE, warning=FALSE}
t<- Correlation(PM$BAM_CSTEP, PM$DT_ILK, PM, lm, 50, 275, 300, "DT_ILK", "BAM_CSTEP")
t
```

## t-test

```{r   message=FALSE, warning=FALSE}
t.test(PM$DT_ILK,PM$BAM_CSTEP )
```

## Box Plot

- DT_ILK: DustTrak 8530 measurements of PM2.5 placed at ILK Labs for everyday 30 mins before and after the rides.

- BAM_CSTEP: BAM 1022 measurements of PM2.5 placed at CSTEP

```{r  message=FALSE, warning=FALSE}
names(PM)<-c("hour", "DT_ILK",  "BAM_CSTEP")
PM_melt<-reshape2::melt(PM, id="hour", measure.vars = c( "DT_ILK",  "BAM_CSTEP") )
names(PM_melt)<-c("hour","Instrument", "PM")
p1<-ggplot(PM_melt, aes(Instrument, PM))+ 
  labs(x="",  y= expression(paste(PM[2.5] ," (", mu, "g",~m^{-3}, ")")),title=paste0(""))+
  stat_summary(fun.data = f, geom="boxplot", width=0.2, size=1.2)+  
  stat_summary(fun.y=mean, colour="black", geom="point",size=4)+
  scale_y_continuous(limits = c(0,200), expand = c(0, 0))+theme_minimal()+
  theme(legend.text=element_text(size=14),plot.subtitle = element_text(size = 10, face = "bold"),
        plot.title = element_text(size = 12, face = "bold"), 
        axis.title = element_text(size=28, face="bold"),axis.text = element_text(size = 28, colour = "black",face = "bold"),
        panel.border = element_rect(colour = "black", fill=NA, size=1.2),axis.text.x = element_blank() ) + annotate("text", label = "DT_ILK", x ="DT_ILK", y =180, size=6, face="bold")+ annotate("text", label = "BAM_CSTEP", x ="BAM_CSTEP", y =180, size=6, face="bold")
p1


```

## Time Variations


```{r   message=FALSE, warning=FALSE}
names(PM)<-c("date", "DT",  "BAM")
timeVariation(PM, pollutant=c("DT",  "BAM"))

```



## Correction of DustTrak 8530 using this equation- y=0.21x+11.1

## Corrected DustTrak Correlation plot

```{r   message=FALSE, warning=FALSE}
names(PM)<-c("date", "DT_ILK",  "BAM_CSTEP")
PM$DT_ILK<-(PM$DT_ILK*0.21)+11.1
t<- Correlation(PM$BAM_CSTEP, PM$DT_ILK, PM, lm, 10, 45, 50, "DT_ILK", "BAM_CSTEP")
t
```

## t-test

```{r   message=FALSE, warning=FALSE}
t.test(PM$DT_ILK,PM$BAM_CSTEP )
```

## Box Plot

- DT_ILK: Corrected DustTrak 8530 measurements of PM2.5 placed at ILK Labs for everyday 30 mins before and after the rides.

- BAM_CSTEP: BAM 1022 measurements of PM2.5 placed at CSTEP

```{r  message=FALSE, warning=FALSE}
names(PM)<-c("hour", "DT_ILK",  "BAM_CSTEP")
PM_melt<-reshape2::melt(PM, id="hour", measure.vars = c( "DT_ILK",  "BAM_CSTEP") )
names(PM_melt)<-c("hour","Instrument", "PM")
p1<-ggplot(PM_melt, aes(Instrument, PM))+ 
  labs(x="",  y= expression(paste(PM[2.5] ," (", mu, "g",~m^{-3}, ")")),title=paste0(""))+
  stat_summary(fun.data = f, geom="boxplot", width=0.2, size=1.2)+  
  stat_summary(fun.y=mean, colour="black", geom="point",size=4)+
  scale_y_continuous(limits = c(0,50), expand = c(0, 0))+theme_minimal()+
  theme(legend.text=element_text(size=14),plot.subtitle = element_text(size = 10, face = "bold"),
        plot.title = element_text(size = 12, face = "bold"), 
        axis.title = element_text(size=28, face="bold"),axis.text = element_text(size = 28, colour = "black",face = "bold"),
        panel.border = element_rect(colour = "black", fill=NA, size=1.2),axis.text.x = element_blank() ) + annotate("text", label = "DT_ILK", x ="DT_ILK", y =45, size=6, face="bold")+ annotate("text", label = "BAM_CSTEP", x ="BAM_CSTEP", y =45, size=6, face="bold")
p1


```

## Time Variations


```{r   message=FALSE, warning=FALSE}
names(PM)<-c("date", "DT",  "BAM")
timeVariation(PM, pollutant=c("DT",  "BAM"))

```